% ------------------------------------------------------------------------------
% Introduction
% ------------------------------------------------------------------------------
\section{Introduction}
\label{sec:introduction}

% ------------------------------------------------------------------------------
% Purpose
% ------------------------------------------------------------------------------
\subsection{Purpose}
\label{sec:purpose}

This document represents the software component of Lanturn, an Autonomous
Underwater Vehicle made by the Robosub Senior Design Software and
Hardware/Electrical teams. This will break down into further sub teams which
put together make up the entire RoboSub Senior Design Software Team. These sub
teams include Autonomy, Computer Vision, Controls, and Navigation. Some modules
used for software include: the ROS module and the Arduino module.
\par

% ------------------------------------------------------------------------------
% Document Conventions
% ------------------------------------------------------------------------------
\subsection{Document Conventions}
\label{sec:conventions}

The standards/conventions that were used to write this document are very common
formatting such as bold headings, highlighted words that are important, and
smaller fonts for paragraphs.
\par

% ------------------------------------------------------------------------------
% Intended Audience and Reading Suggestions
% ------------------------------------------------------------------------------
\subsection{Intended Audience and Reading Suggestions}
\label{sec:audience}

The types of readers that this document is intended for are future developers
of the RoboSub Senior Design years, developers who are interested in robotics,
and hobbyists.  This document will cover the four different sub teams that make
up the RoboSub Senior Design Team working on Lanturn: Autonomy, Computer
Vision, Controls, and Navigation. 
\par

Autonomy covers state machines, Computer Vision covers machine learning and
image processing, Controls covers movement and IMU readings, Navigation covers
sensor readings and mapping/localization.
\par

% ------------------------------------------------------------------------------
% System Overview
% ------------------------------------------------------------------------------
\subsection{System Overview}
\label{sec:overview}
The Autonomy/Mission Planning sub team is to cover the SMACH model developed to
control the AUV subsystems through each task at the RoboNation Competition.  
\par

The Computer Vision sub team is to recognize specific images, such as badges or
dollar signs, in underwater environments and then process them through a
machine learning model and send the relevant data to Autonomy/Mission Planning. 
\par

The Controls sub team is to control Lanturn, the sub, with its thrusters using
PID controllers. This is done using three different axes: Pitch to tilt forward
or backward, roll to move side to side, and Yaw to rotate left or right.  
\par

The Navigation sub team is to gather data from the sensors such as barometer
and then also send relevant data to Autonomy/Mission Planning. 
\par
 
