% ------------------------------------------------------------------------------
% Policy and Tactics
% ------------------------------------------------------------------------------
\section{Policies and Tactics}
\label{sec:policies}

The main influences on Lanturn’s Software design has already been established
by previous years. 
\par

Some adjustments have been made by individuals to suit their ideas and
programming style, but most of the system is inherited from previous years.
\par

% ------------------------------------------------------------------------------
% Specific Product Used
% ------------------------------------------------------------------------------
\subsection{Specific Product Used}
\label{sec:specific}

\begin{itemize}
    \item System 
        \begin{itemize}
            \item Operating System 
            \item Ubuntu 20.04 
            \item Build System 
            \item Colcon 
            \item Ament\_cmake 
        \end{itemize}

    \item Autonomy 
        \begin{itemize}
            \item Visual Studio Code 
            \item Groot 
            \item SMACH 
            \item BehaviorTree.CPP 
        \end{itemize}

    \item Controls 
        \begin{itemize}
            \item Visual Studio Code 
            \item Platform.I0 
        \end{itemize}

    \item Computer Vision 
        \begin{itemize}
            \item LabelIMG 
            \item Google CoLab 
            \item YOLOv4 
            \item Darknet 
            \item OpenCV 
        \end{itemize}

    \item Mapping and Localization 
        \begin{itemize}
            \item Gazebo 
            \item Visual Studio Code 
            \item Cubik Studio
        \end{itemize}
\end{itemize}

% ------------------------------------------------------------------------------
% Requirements Traceability
% ------------------------------------------------------------------------------
\subsection{Requirements Traceability}
\label{sec:traceability}

Each module of the system will have its own git repository. The sub-team
assigned to the module will be responsible for keeping detailed documentation
for the process of setting up, installing and using the software module.
\par

% ------------------------------------------------------------------------------
% Testing the Software
% ------------------------------------------------------------------------------
\subsection{Testing the Software}
\label{sec:testing}

\begin{itemize}
    \item Navigation 
        \begin{itemize}
            \item Create Gazebo Simulation for localization testing 
            \item Unit test for processing sensor data 
            \item Unit test for noise filter on sensor data 
            \item Unit test for publishing position data 
            \item Unit test for subscribing to position data 
        \end{itemize}

    \item Autonomy 
        \begin{itemize}
            \item Create unit test for states.  
            \item Create unit test for publishers 
            \item Create unit test for subscribers. 
            \item Simulate test environment for states 
            \item Simulate test environment for publishers 
            \item Simulate test environment for subscribers 
            \item Use testing AUV (Blastoise)
        \end{itemize}
\end{itemize}

% ------------------------------------------------------------------------------
% Engineering Trade-Offs
% ------------------------------------------------------------------------------
\subsection{Engineering Trade-Offs}
\label{sec:tradeoffs}

ROS is the leading opensource robotics software in use today. There are no
engineering tradeoffs with hardware and software support being
mutigenerational. 
\par

% ------------------------------------------------------------------------------
% Guidelines and Conventions
% ------------------------------------------------------------------------------
\subsection{Guidelines and Convetions}
\label{sec:guidelines}

Using the selected IDE and choice of CPP instead of python ensures that the
languages general convention is enforced.
\par

% ------------------------------------------------------------------------------
% Protocols
% ------------------------------------------------------------------------------
\subsection{Protocols}
\label{sec:protocols}

By using ROS the built in API of the standardized subscriber and publisher
model is always enforced.
\par

% ------------------------------------------------------------------------------
% Maintaining the Software
% ------------------------------------------------------------------------------
\subsection{Maintianing the Software}
\label{sec:maintain}

No plans to maintain software, only fix bugs. The software is specially
attached to the hardware, the only way to maintain software or update is to
upgrade hardware. If we do that then we need to refactor or use a different ROS
version.
\par

% ------------------------------------------------------------------------------
% Interfaces
% ------------------------------------------------------------------------------
\subsection{Interfaces}
\label{sec:interfaces}

There is no interface for users, fully autonomous, web GUI subscribes to
publishers for user visualization.
\par

% ------------------------------------------------------------------------------
% System Deliverables
% ------------------------------------------------------------------------------
\subsection{System Deliverables}
\label{sec:deliverables}

% ------------------------------------------------------------------------------
% Abstractions
% ------------------------------------------------------------------------------
\subsection{Abstractions}
\label{sec:abstractions}

