% ------------------------------------------------------------------------------
% User Interface
% ------------------------------------------------------------------------------
\section{User Interface}
\label{sec:userinterface}

% ------------------------------------------------------------------------------
% Overview of User Interface
% ------------------------------------------------------------------------------
\subsection{Overview of User Interface}
\label{sec:overviewui}

At the end of this project, there will be a custom user interface designed
specifically for Lanturn to aid in interacting with the running ROS system. 
\par

While custom interfaces are implemented, there are already implemented ROS
integrated User Interfaces, RQT and Rviz.  
\par

RQT is the one that can be used by any ROS system and be the one that will be
demonstrated here.
\par

% ------------------------------------------------------------------------------
% Screen Frameworks or Images
% ------------------------------------------------------------------------------
\subsection{Screen Frameworks or Images}
\label{sec:frameworks}

% ------------------------------------------------------------------------------
% RQT
% ------------------------------------------------------------------------------
\subsubsection{RQT}

RQT is a user interface that comes packages with ROS and other visualization
tools. Ir can be used to read, send and interpret data. It allows a user to
interact with the ROS system the GUI is connected to. It uses the concepts of
plugins to allow the user to view different forms of data and interpret them in
different ways. 
\par

In this image, there are six plugins open. 
\begin{enumerate}
    \item Top Left. The Process Monitor plugin helps the user see all processes interacting with or through the ROS system. 
    \item Top Center. The MatPlot plugin can interpret data in a grid form and, in the context of Lanturn, it can be used to interpret stability, velocity and other odometry data. 
    \item Top Right. The Message Publisher allows the user to send different messages to nodes in the ROS system. 
    \item Bottom Right. The Console plugin displays log messages the nodes in the ROS system are saving. 
    \item Bottom Center. The Image View plugin displays images that are being streamed through a topic. 
    \item Bottom Right. The Topic Monitor shows the topics in the current ROS system and allows users to see what messages are going through the topic.
\end{enumerate}

% ------------------------------------------------------------------------------
% User Interface Flow Diagrams
% ------------------------------------------------------------------------------
\subsection{User Interface Flow Diagrams}
\label{sec:flowdiagrams}

The RQT user interface uses plugins to display information giving the user full
control as to what is displayed and what is not. This means the user decides on
the flow of the user interface, meaning, any flow diagram displayed here would
miss the point of the modularity of this user interface design.
\par

